A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-04 manuscript.Rmd
some more suggestions re modeling

t-test

@@

But then you realize that the new literature suggests that there could be a bias in measurement:

@@

Multigroup CFA + Measurement Invariance

@@

Commit this version:

```r
# -- type this on the R console --
gert::git_add("idea.md")
gert::commit("exclude bias in measurement as possible confounder")
```

@@

It is probably better to assume more pessimistic values.
This way, we make sure that our analytic strategy is viable even in non-optimal circumstances.
Therefore, we will assume that the loadings are 30% lower than reported and that the standardized mean difference is only 0.2.
These assumption can be simply translated into [`lavaan` [@R-lavaan]](https://lavaan.ugent.be)[^lavaan] model syntax:

@@

From which we can simulate data:

>>>>

Independent t-test

@@

Now assume that after discussing with your colleagues, you settle onto a final analysis strategy using latent variable models with tests for measurement invariance because power is greater and you want to exclude bias in measurement as possible confounder <!-- Aaron, reference needed-->. This results in changes to your notes as follows:

@@

Multigroup Confirmatory Factor Analysis
First, establish strong measurement invariance using a CFI cutoff-criterion
Second, test for differences in latent factor means of Machiavellianism using a $\chi^2$ test

@@

Again, stage the changes to this file and commit like before using `git_add()` and `git_commit()` or use the following shorthand to stage all new and modified files and then commit:

```r
# -- type this on the R console --
gert::commit_all("switch to CFA to exclude bias in measurement as possible confounder")
```

@@

Typically, it is recommended to choose conservative values during study design planning  [@brandmaier2018precision].
This way, we make sure that our analytic strategy is viable even in non-optimal circumstances, for example if the measurement instrument works less well then expected or the population characteristics are more different than expected.
As a heuristic guess, we assume that the factor loadings are 30% lower than reported and that the standardized mean difference is only 0.2.
These assumption can be simply translated into [`lavaan` [@R-lavaan]](https://lavaan.ugent.be)[^lavaan] model syntax:

@@

Structural Equation Models are generative models that not only fit models but lend themselves to data simulation. This is particularly easy in lavaan syntax using the function `simulateData`.
